Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-04-09 dictionary.tex
Made some subsections

%\begin{acknowledgements}
\subsection*{Acknowledgements}
We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves; their knowledge and help have been invaluable.
We also thank Takashi Suzuki, who

We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
and the National Science and Engineering Research Council,
as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.

@@

\section{Quasicharacter sheaves}

@@

\section{Bounded and Finite quasicharacter sheaves}%\label{sec:bounded}

@@

\section{Connected commutative algebraic groups} \label{sec:connected}

@@

\section{Commutative \'etale group schemes} \label{sec:etale}

\subsection{Definition, revisited}

@@

\section{Right-Exactness of the component group sequence} \label{sec:restriction}

@@

\section{The function--sheaf dictionary for smooth, commutative group schemes}
\label{sec:snake}

>>>>

%\begin{acknowledgements}
\subsection*{Acknowledgements}
We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
quasicharacter sheaves; their knowledge and help have been invaluable.
We also thank Takashi Suzuki, who made many helpful observations and suggestions.
%
Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
and the National Science and Engineering Research Council,
as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.

@@

\section{The category of quasicharacter sheaves}

@@

\section{Two special subcategories of quasicharacter sheaves}%\label{sec:bounded}

@@

\section{The case of connected commutative algebraic groups} \label{sec:connected}

@@

\section{The case of \'etale commutative group schemes} \label{sec:etale}

\subsection{Quasicharacter sheaves, revisited}

@@

\section{The main result}

\subsection{The component group sequence} \label{sec:restriction}

@@

\subsection{The function--sheaf dictionary for smooth, commutative group schemes}
\label{sec:snake}
